---
title       : Automatic Versus Manual Which one is better for mpg
subtitle    : 
author      : Shobeir
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Motor Trend Car Road Tests

### Description

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).


[, 1]	 mpg	 Miles/(US) gallon
[, 2]	 cyl	 Number of cylinders
[, 3]	 disp	 Displacement (cu.in.)
[, 4]	 hp	 Gross horsepower
[, 5]	 drat	 Rear axle ratio
[, 6]	 wt	 Weight (1000 lbs)
[, 7]	 qsec	 1/4 mile time
[, 8]	 vs	 V/S
[, 9]	 am	 Transmission (0 = automatic, 1 = manual)
[,10]	 gear	 Number of forward gears
[,11]	 carb	 Number of carburetors
Source

Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.

--- .class #id 

## Summary of Regression Model

Based on the coefficients, it seems that with moving from automatic to manual 2.5 units increase in the `mpg` accounting for all the other parameters. Now, we build 5 models with `am`, `wt` (weight), `qsec` (1/4 mile time), and `cyl` (number of cylinders).

```{r}
data("mtcars")
summary(lm(mpg ~ ., data = mtcars))$coefficients
```

---

## Exploratory Plot

```{r echo=FALSE, message=FALSE}
data("mtcars")
library("ggplot2")
library("GGally")
ggpairs(mtcars, colour='am', alpha=0.4)
```


---
## Shiny App

The Shiny App uses three of the most important factors to plot their effects on `mpg` with respect to the `automatic` versus `manual` transmission.
The app can be found here at:
[Slidify App](https://shobeir.shinyapps.io/data_product/)





